

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->
The first thing, as always, is to set the working directory. 

<!--
Read in the homework6.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
The fabricated data are supposed to approximate how people perform
in different types of visual searches. Specifically, we're 
comparing performance in feature searches (e.g. looking for a red
X among green Xs) and conjunction searches (e.g. looking for a red
X among green Xs and red Os). We're also looking at how the number
of distractors within the search display effect our data.
-->
I read in the homework for this assisgnment. 

```{r}
dat<-read.csv("homework6.csv")
```


<!--
Check the structure of the data and change any variables that should
be factor variables into factor variables
-->

The next step is to check out the structure
```{r}
str(dat)
```
From the structure we can see that position, subject, and subject2
should all be factor variables. So let's fix that.


```{r}
dat$distractors<-as.factor(dat$distractors)
dat$subject<-as.factor(dat$subject)
dat$subject2<-as.factor(dat$subject2)
```

First we need to get only the data from the conjunction searches.

```{r}
temp<-dat[dat$type=="conjunction",]
```
Now we can run our ANOVA.
<!--
Perform a one-way between-subjects ANOVA examining for effects of 
the the number of distractors for the conjunction searches only.
Also create a line graph to help you interpret the results of your
analysis.
-->
```{r}
summary(aov(rt~distractors, data=temp))
```
There's a significant effect of which position a word appears in on
a list, F(2,21) = 8.603, p < .01. To interpret these data better,
I'll create a line graph that shows the percent recalled for the
various list positions when participants are distracted.
```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```
```{r}

temp<-temp%>%group_by(distractors)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(rt)))

f<-ggplot(temp, aes(x=as.factor(distractors),
                    y=means,
                    group=1))+
  geom_line(size=1)+
  geom_point(size=2)+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Effect of Distractors on Performance")+
  labs(x="Distractors",y="Performance Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```

This figure shows that as the number of distractors increase, the performance times on the task increase which concludes that there is lower level of performance as the distractors increase.
<!--
Perform a one-way within subjects ANOVA on the same data you analyzed
earlier. Tip: use subject as the subjects variable for this analysis.
-->
```{r}
temp<-dat[dat$type=="conjunction",]
```
I am now able to the within-subjects analysis.

```{r}
summary(aov(rt~distractors+
              Error(subject/distractors),data=temp))
```

The results state that there was a significant difference. The results are F(2,14) = 56.0, p < .001. The subjects with more distractors were slower and the subjects with fewer distractors were able to perform better. 

<!--
Perform a between-subjects ANOVA examining for the effects of and
interactions between the number of distractors and the search type.
Make sure to interpret your results.
-->
I will now perform a between-subjects 2-way ANOVA looking for the 
effects of and interactions between the number of distractors and 
the search type. 

```{r}
summary(aov(rt~distractors*type, data=dat))
```
The analyses show that there was an effect of distractors, F(2,42) =
2.6, p < .10. There was also an effect of type, F(1,42) =
459.4, p < .001. There was also an interaction between distractors and
type, F(2,42) = 7.8, p < .01.

<!--
Create a line graph and a grouped bar graph to help us interpret
the results of the previous analyses. Include error bars in your
figures.
-->
To help me interpret the earlier analyses, I'll create line and
grouped bar graphs for the data I analyzed. But first I need to
summarize the data.

```{r}
temp<-dat%>%group_by(distractors,type)%>%
  summarize(means=mean(rt),
            sems=sd(rt)/sqrt(length(n)))
```
```{r}
f<-ggplot(temp, aes(x=distractors,
                    y=means,
                    group=type,
                    color=type))+
  geom_line(size=1)+
  geom_point(size=2)+
  scale_color_manual(values=c("darkgreen","red"),
                     name="Type",
                     breaks=c("conjunction","feature"),
                     labels=c("conjunction", "feature"))+
  geom_errorbar(aes(ymax=means+sems, ymin=means-sems),width=.2)+
  ggtitle("Performance by Type with Distractors")+
  labs(x="Distractors",y="Performance Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f

f<-ggplot(temp, aes(x=distractors,
                    y=means,
                    fill=type))+
  geom_bar(stat="identity",position=position_dodge())+
  scale_fill_manual(values=c("darkgreen","red"),
                     name="Type",
                     breaks=c("conjunction","feature"),
                     labels=c("conjunction", "feature"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2,
                position=position_dodge(.9))+
  ggtitle("Performance by Type with Distractors")+
  labs(x="Distractors",y="Performance Time")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.76))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f
```

<!--
Interpret the statistical results in light of the figures.
-->
From the figures and earlier analyses we can see that as number of distractors increased as well as the time needed to respond increased for a search type. The more distractors there were, the longer the response time was. The response times were also affected as the feature type was able to have a decreased time although they still had distractors. 

<!--
Perform a within-subjects two-way ANOVA examining for the effects
of and interactions between number of distractors and search type.
Tip: use subject as the subject's variable for this analysis.
Interpret the results of the analysis based on the statistical
results and your earlier figures.
-->
Here I'm performing a within-subjects two-way ANOVA to examine for
the effects of and interactions between number of distractors 
and search type.

```{r}
summary(aov(rt~distractors*type+ 
               Error(subject/(distractors*type)),data=dat))
```
From the analyses and the figures, we can see that generally people were worse with the increased distractors F(2,14) = 11.2, p < .01. People generally perform with a shorter response time in feature versus conjunction F(1,7) = 1626, p < .001. Participants in the feature search type slowed their response time as the number of distractors increased, F(2,14) = 32.1, p < .05

<!--
Finally conduct and interpret the results of a mixed ANOVA in which
number of distractors varies within subjects and the type of search
varies between subjects. Make sure to interpret your results. Tip:
use subject2 as your subject's variable for this analysis.
-->
Finally, I'll conduct a mixed ANOVA in which number of distractors varies within subject and the type of search varies bewteen subjects.

```{r}
summary(aov(rt~distractors*type+
              Error(subject2/distractors),
            data=dat))
```

From our analyses, we can see that the number of distractors effected participants response time in the feature search type, F(1,14) = 182.4, p < .05. Additionally, we see that participants in the feature search type decreased response time as the number of distractors increased, F(2,28) = 11.0, p < .05. Finally there is also a significant effect between distractors and the search type F(2,28) = 32.5, p < .05. 


