## Homework 4

<!--
Remember you can use the example4.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework4.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->
```{r}
dat<-read.csv("homework4.csv")
```

```{r}
str(dat)
```


<!--
Check the structure of the data.
-->
'data.frame':	80 obs. of  2 variables:
 $ condition: Factor w/ 2 levels "control","experimental": 2 1 2 1 2 1 2 1 2 1 ...
 $ agreement: Factor w/ 2 levels "no","yes": 1 1 2 2 1 1 2 2 1 2 ...

There are two variables, condition and agreement

<!--
Create a table that shows how many people fell into each category.
-->

```{r}
table(dat$condition, dat$agreement)
```

From examining the table, it appears that there might more agreements
with the expieremental versus the controls. 
<!--
Perform a chi-square test to determine whether or not the experimental
conditions and agreement with a statement are independent or related.
Also, interpret the results of your test and provide a a statistical
statement that supports your interpretation. As there's no way to
insert the chi-square symbol, you can just use chi-square instead
(see example4.Rmd).
-->
To determine if the data support the appearance of a relationship
between gender and major, I performed a chi-square test.
```{r}
chisq.test(dat$condition,dat$agreement)
```
According to the results of the chi-square test, major and gender
are independent of one another Chi-square(1) = 1.2788, p = .258.
